---
title: Tidytuesday - Art collection
author: 'Inchul'
date: '2021-01-18'
slug: []
categories:
  - R
tags:
  - tidytuesday
Description: ''
Tags: []
Categories: []
DisableComments: no
---

I have started the **tidytueseday** - which is comunity for R tidyverse user.
With this, I can train myself to be good data handler, I think. 

- Datalink url : https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-01-12/readme.md


Let's start - 

# My questions 
- any trend for male/female over time
- nation of artists
- artwork size over time
- medium for artwork over time

# Exploration

```{r}
library(tidyverse)
theme_set(theme_light())
```


```{r}
artwork <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-12/artwork.csv')
artists <- readr::read_csv("https://github.com/tategallery/collection/raw/master/artist_data.csv")
```


# Artist 

```{r}
artwork %>%
  View()

artists %>% View()

artists %>%
  count(yearOfBirth,name, sort=TRUE) %>%
  filter(is.na(yearOfBirth)) %>%
  View()

artists %>%
  mutate(birth=10*(yearOfBirth %/% 10)) %>%
  count(birth, gender, sort=TRUE) %>%
  na.omit() %>%
  ggplot(aes(birth, n, fill=gender)) +
  geom_col(position = "dodge") + 
  labs(title="Artist birth")

```


```{r}

artists %>%
  filter(!is.na(placeOfBirth)) %>%
  extract(placeOfBirth, into=c("city", "nation"), "(.*), (.*)") %>%
  filter(!is.na(city)) %>%
  mutate(nation=fct_lump_n(nation, 30),
         year= 10*(yearOfBirth %/% 10)) %>%
  count(year, nation) %>%
  ggplot(aes(n, fct_reorder(nation,n), fill=year)) +
  geom_col() +
  labs(title="artist nation",
       x="cases",
       y="nation")

#mostly UK artist??
artists %>%
  na.omit() %>%
  extract(placeOfBirth, into=c("city", "nation"), "(.*), (.*)") %>%
  filter(!is.na(city)) %>%
  mutate(nation=fct_lump_n(nation, 30),
         year= 10*(yearOfBirth %/% 10)) %>%
  count(year, nation) %>%
  ggplot(aes(n, fct_reorder(nation,n))) +
  geom_col() +
  facet_wrap(year~., scales="free") +
  labs(title="artist nation over time",
       x="cases",
       y="nation")


```


# Artwork
```{r}
artwork %>%
  mutate(artist=fct_lump_n(artist,20)) %>%
  count(artist, sort=TRUE) 

artwork %>%
  mutate(artist=fct_lump_n(artist,20)) %>%
  filter(!is.na(year), artist!="Other") %>%
  ggplot(aes(year, fct_reorder(artist, -year))) +
  geom_point(alpha=0.3) +
  labs(title="artist working year",
       y="Artist")

```


It seems there is no correlation between size and time. But if we cut down from 1800, we can see there's some relation of the artwork size over time
```{r}
# no relation size and year 
artwork %>%
  select(year, width, height) %>%
  mutate(size = width * height / 100,
         year = 10 * (year %/% 10)) %>%
  filter(!is.na(year),
         size < 500000) %>%
  ggplot(aes(as.factor(year), size)) +
  geom_boxplot(na.rm = TRUE) + 
  geom_point(alpha=0.3) +
  scale_y_log10()



# if we cut 1800
# plot of the size trend (idea from https://josephlewis.github.io/aspect.html)

artwork %>%
  select(year, width, height) %>%
  mutate(size = width * height / 100,
         year = 10 * (year %/% 10)) %>%
  filter(!is.na(year),
         year > 1800,
         size < 500000) %>%
  group_by(year) %>%
  summarise(width = mean(width),
            height = mean(height)) %>%
  ggplot(aes(xmin = 0, xmax = width, ymin = 0, ymax = height, color=year)) +
  geom_rect(alpha=0) +
  facet_wrap(~year) +
  labs(title = "artwork size over time",
       subtitle = "only from 1800 yr")
```

```{r}

options(scipen = 99)

artwork %>% 
  select (year, medium) %>%
  extract(medium, c("medium1", "medium2"), "(.*) on (.*)") %>%
  mutate(year = 10 * (year %/% 10),
         year = as.factor(year),
         medium = fct_lump_n(medium1, 30)) %>%
  filter(!is.na(medium),
         medium != "Other") %>%
  count(medium, sort=TRUE) %>%
  ggplot(aes(n,fct_reorder(medium,n))) + 
  geom_col() +
  labs(title="general medium over all the time")


# careful to use 'distict' 
artwork %>% 
  select (year, medium) %>%
  filter(year> 1700) %>%
  extract(medium, c("medium1", "medium2"), "(.*) on (.*)") %>%
  mutate(year = 10 * (year %/% 10),
         year = as.factor(year),
         medium = fct_lump_n(medium1, 20)) %>%
  filter(!is.na(medium),
         medium != "Other") %>%
  add_count(year, medium) %>%
  distinct(year,medium, n) %>%
  ggplot(aes(n,fct_reorder(medium,n))) + 
  geom_col() +
  facet_wrap(year~., scale="free") +
  labs(title=" medium over decade")


```




