---
title: Yarn RM analysis
author: ''
date: '2021-10-12'
slug: []
categories: []
tags:
  - R
  - rstat
  - ggplot
  - yarn
  - rm
Description: ''
Tags: []
Categories: []
DisableComments: no
---

I found a useful link when I just am browsing internet. it's related to Yarn Resource Manager analysis using drill.
You know drill support no schema data reading. if you are ingested in that, go to http://www.openkb.info/2016/10/how-to-use-drill-to-parse.html

working process is like : 

 1) request rest api to RM
 2) download Json data
 3) read the json data by drill
 
 

It's cool. But I want more than that. So I thought it would be cool if I can code R for it. 
Because there is super cool R pakcage `rvest` to connect/fetch data through rest api. 

If you have unsecure yarn RM, this is enough for you. But if it's secure, you cannot use `rvest` becuase of Certificate SSL stuff. 

I don't like it, but I should download the json file manually and code R. :( 

## how to download json from RM

use `curl`

```{undefined eval=FALSE, include=FALSE}

$ curl -v -X GET -H "Content-Type: application/json" https://`hostname -f`:8090/ws/v1/cluster/apps -u id:pw -k

```


now you got ready to start off!! let's kick off. 


## Loading json file

I used `jsonlite` and `pluck` to extract data. 

```{r}
library(tidyverse)
library(rvest)
library(scales)
theme_set(theme_light())

library(jsonlite)

raw_json <- jsonlite::fromJSON("C:/dev/R_Analysis/rm.json")
```

```{r}
app_jobs <- pluck(raw_json, 'apps', 'app') %>%
  as_tibble() %>% 
  select (id, user, name,queue, state, finalStatus, startedTime, finishedTime, elapsedTime, allocatedVCores, allocatedMB)


app_jobs %>%
  count(state)
```


## job time variance
```{r}

#options(scipen=10)

app_jobs  %>%
  mutate (new= (finishedTime - startedTime)) %>%
  mutate(user=fct_reorder(user, desc(elapsedTime))) %>%
  ggplot(aes(x=user, y=elapsedTime, color=user)) +
  geom_boxplot() +
  geom_point() +
  coord_flip() +
  scale_y_log10(label=scales::comma_format(), limits=c(1000,NA)) +
  #scale_y_continuous(label=comma_format()) +
  labs(title="job time variance",
    y="")

```


```{r}
app_jobs %>% 
  as_tibble() %>%
  ggplot(aes(x=user, y=elapsedTime, color=user)) +
  geom_boxplot() +
  scale_y_log10(label=comma_format()) +
  #geom_text(aes(label=id)) +
  facet_grid(queue~state) 

```

### job # over time

```{r}
library(lubridate)

app_jobs %>%
  select(startedTime, finishedTime, elapsedTime,allocatedVCores,user) %>%
  mutate(startedTime= lubridate::as_datetime(startedTime/1000),
         finishedTime= lubridate::as_datetime(finishedTime/1000),
         elapsedTime= lubridate::as_datetime(elapsedTime/1000),
         date=lubridate::as_date(startedTime)) %>%
  count(date,user) %>%
  ggplot(aes(x=date, y=n, color=user)) +
  geom_line() +
  labs(y="job #", 
       title="job # over date")

```

```{r}
app_jobs %>%
  select(startedTime, finishedTime, elapsedTime,allocatedVCores,user) %>%
  mutate(startedTime= lubridate::as_datetime(startedTime/1000),
         finishedTime= lubridate::as_datetime(finishedTime/1000),
         elapsedTime= lubridate::as_datetime(elapsedTime/1000),
         date=lubridate::as_date(startedTime)) %>%
  group_by(date, user) %>%
  filter(allocatedVCores != -1)
```


### average job time
```{r}
app_jobs %>%
  select(startedTime, finishedTime, elapsedTime,allocatedVCores,user) %>%
  mutate(startedTime= lubridate::as_datetime(startedTime/1000),
         finishedTime= lubridate::as_datetime(finishedTime/1000),
         elapsedTime= lubridate::as_datetime(elapsedTime/1000),
         date=lubridate::as_date(startedTime),
         sec = seconds(elapsedTime)) %>%
  group_by(date,user, avb_sec=mean(sec)) %>%
  ggplot(aes(date,avb_sec,color=user)) +
  geom_line() +
  scale_y_time() +
  labs(y="average second")
  
```
```{r}
app_jobs %>%
  select(startedTime, finishedTime, elapsedTime,allocatedVCores,user,state) %>%
  mutate(startedTime= lubridate::as_datetime(startedTime/1000),
         date=lubridate::as_date(startedTime)
         ) %>%
  count(date,state) %>%
  ggplot(aes(date,n,color=state)) +
  geom_line() +
  scale_x_time() +
  labs(y="average second")

```


