---
title: Amazone Seller choice
author: ''
date: '2021-01-21'
slug: []
categories:
  - R
tags:
  - rstat
Description: ''
Tags: []
Categories: []
DisableComments: no
---

If you are a fan of Baysian, you may be interested in this [post](https://www.johndcook.com/blog/2011/09/27/bayesian-amazon/).
This post is about Amazon seller choice. 

In my case, if there are so many similar choices, I cannot do it. :( 
But, if you are a Baysian, you can choose best one from them. (Yes, I am not smart)

Let's say we know sellers like 

* 94% positive out of 85,193 reviews
* 98% positive out of 20,785 reviews
* 99% positive out of 840 reviews

Which seller do you want to choose?

Let's assume the all vote rate is *nomal distribution*. 

## review count

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```


```{r}

a_pos <- round(85193 * 0.94)
a_neg <- 85193 - a_pos


b_pos <- round(20785 * 0.98)
b_neg <- 20785 - b_pos

c_pos <- round(840 * 0.99)
c_neg <- 840 - c_pos
```

Assume the priority as uniform distribution `(1,1)` - all *possibility* are same. 

```{r}
#pri probabailty
seller_beta <- tibble(prob = seq(0, 1, length = 100)) %>% 
  mutate (a_seller = dbeta(prob, 1,1),
          b_seller = dbeta(prob, 1,1),
          c_seller = dbeta(prob, 1,1))

seller_beta %>%
  ggplot(aes(x=prob)) +
  geom_line(aes(y=a_seller, color="a")) +
  geom_line(aes(y=b_seller, color="b")) +
  geom_line(aes(y=c_seller, color="c")) 


```

Long story shorter, *beta* distribution is a pair with *normal distribution.* 

```{r}

seller_beta %>% 
  mutate (a_seller = dbeta(prob, a_pos+1,a_neg+1),
          b_seller = dbeta(prob, b_pos+1,b_neg+1),
          c_seller = dbeta(prob, c_pos+1,c_neg+1)) %>% 
  pivot_longer(cols=a_seller:c_seller, names_to = "seller") %>%
  ggplot(aes(x=prob, value, color=seller)) +
  geom_line() +
  facet_wrap(seller~., nrow=3, scales="free_y") +
  theme(legend.position = "none")



```

## mean/variance of the vote rate

The mean of the beta distribution is `a/(a+b)` and the variance is `ab/((a+b)^2 (a+b+1))`


```{r}

df <- tibble(
  a_mean = a_pos+1 /(a_pos+1 + a_neg+1 ),
  a_var = (a_pos+1)*(a_neg+1)/(a_pos+1+a_neg+1)^2*(a_pos+1 + a_neg+1 +1),
  b_mean = b_pos+1 /(b_pos+1 + b_neg+1 ),
  b_var = (b_pos+1)*(b_neg+1)/(b_pos+1+b_neg+1)^2*(b_pos+1 + b_neg+1 +1),
  c_mean = c_pos+1 /(c_pos+1 + c_neg+1 ),
  c_var = (c_pos+1)*(c_neg+1)/(c_pos+1+c_neg+1)^2*(c_pos+1 + c_neg+1 +1))


options(scipen = 99)
  
df %>%
  select(ends_with("var")) %>%
  pivot_longer(cols=a_var:c_var, names_to = "stat") %>%
  arrange(desc(value)) 

  
```



```{r}
by_seller <- df %>%
  pivot_longer(cols=everything(), 
               names_to = c("seller", "stat"), 
               names_pattern="(.*)_(.*)", 
               values_to="value") 

by_seller %>%
  ggplot(aes (seller, value, color=stat)) +
  geom_point(size = 4, alpha=0.5)  + 
  facet_wrap(stat~., scale="free_y")
```

*seller C*'s *variance* is the smallest. It means that the service of *C* is vary consistency.  
